---
title: "Experimental Data Inspection and Illustrations"
author: "Anton Drasbæk"
date: "10/20/2022"
output: html_document
---
# Description
This R-markdown is used to process, inspect and illustrate data from participants in Experiment A. The data is directly accessed through an API from SoSciSurvey. 

It can be seperated into the following sections after this description:
1) Loading Packages and Data
2) Preprocessing
3) Early Inspections
4) Detailed Plotting
5) Statistical Evaluations

# Load Packages and Data
## Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(httr, tidyverse, cvms, lme4)
```

## Load data
```{r}
api.link <- "https://www.soscisurvey.de/nyheder-kunstig-intelligens/?act=VZcjsI0nAldCV1mJx2etluzi"
api.response <- httr::GET(api.link)

data <- read.csv(text = httr::content(api.response, as = "text"), sep = "\t", na.strings = "") # read in dataframe
rm(api.link, api.response)
```

# Preprocessing
Remove irrelevant columns
```{r}
data <- data %>% 
  select(-SERIAL, -REF, -QUESTNNR, -STARTED, -C003, -C003_01, -D102, -R001_CP, 
         -TIME001, -TIME003, -TIME004, -TIME005, -TIME006, -TIME007, -TIME008, -TIME009,
         -TIME010, -TIME011, -TIME012, -TIME013, -TIME014, -TIME015, -TIME016, -TIME017,
         -TIME018, -TIME019, -TIME020, -TIME021, -TIME022, -TIME023, -TIME024, -TIME002,
         -TIME_SUM, -MAILSENT, -LASTDATA, -Q_VIEWER, -LASTPAGE, -MAXPAGE, -FINISHED, -D001
         )
```

Remove NAs
```{r}
data <- data %>% drop_na(D103)
```


Rename columns to prepare for reshape
```{r}
data <- data %>% 
  rename("AA_01" = "AA01", "AA_02" = "AA02",
         "AA_03" = "AA03", "AA_04" = "AA04",
         "AA_05" = "AA05", "AA_06" = "AA06",
         "AA_07" = "AA07", "AA_08" = "AA08",
         "AA_09" = "AA09", "AA_10" = "AA10",
         "AA_11" = "AA11", "AA_12" = "AA12",
         "AA_13" = "AA13", "AA_14" = "AA14",
         "AA_15" = "AA15", "AA_16" = "AA16",
         "CO_01" = "Q201_01", "CO_02" = "Q202_01",
         "CO_03" = "Q203_01", "CO_04" = "Q204_01",
         "CO_05" = "Q205_01", "CO_06" = "Q206_01",
         "CO_07" = "Q207_01", "CO_08" = "Q208_01",
         "CO_09" = "Q209_01", "CO_10" = "Q210_01",
         "CO_11" = "Q211_01", "CO_12" = "Q212_01",
         "CO_13" = "Q213_01", "CO_14" = "Q214_01",
         "CO_15" = "Q215_01", "CO_16" = "Q216_01",
         "LA_01" = "Q301", "LA_02" = "Q302",
         "LA_03" = "Q303", "LA_04" = "Q304",
         "LA_05" = "Q305", "LA_06" = "Q306",
         "LA_07" = "Q307", "LA_08" = "Q308",
         "LA_09" = "Q309", "LA_10" = "Q310",
         "LA_11" = "Q311", "LA_12" = "Q312",
         "LA_13" = "Q313", "LA_14" = "Q314",
         "LA_15" = "Q315", "LA_16" = "Q316",
         "FA_01" = "Q401", "FA_02" = "Q402",
         "FA_03" = "Q403", "FA_04" = "Q404",
         "FA_05" = "Q405", "FA_06" = "Q406",
         "FA_07" = "Q407", "FA_08" = "Q408",
         "FA_09" = "Q409", "FA_10" = "Q410",
         "FA_11" = "Q411", "FA_12" = "Q412",
         "FA_13" = "Q413", "FA_14" = "Q414",
         "FA_15" = "Q415", "FA_16" = "Q416"
         )

data <- reshape(data, varying = c("AA_01", "AA_02", "AA_03", "AA_04",
                                  "AA_05", "AA_06", "AA_07", "AA_08",
                                  "AA_09", "AA_10", "AA_11", "AA_12",
                                  "AA_13", "AA_14", "AA_15", "AA_16",
                                  "CO_01", "CO_02", "CO_03", "CO_04",
                                  "CO_05", "CO_06", "CO_07", "CO_08",
                                  "CO_09", "CO_10", "CO_11", "CO_12",
                                  "CO_13", "CO_14", "CO_15", "CO_16",
                                  "LA_01", "LA_02", "LA_03", "LA_04",
                                  "LA_05", "LA_06", "LA_07", "LA_08",
                                  "LA_09", "LA_10", "LA_11", "LA_12",
                                  "LA_13", "LA_14", "LA_15", "LA_16",
                                  "FA_01", "FA_02", "FA_03", "FA_04",
                                  "FA_05", "FA_06", "FA_07", "FA_08",
                                  "FA_09", "FA_10", "FA_11", "FA_12",
                                  "FA_13", "FA_14", "FA_15", "FA_16"), direction = "long", idvar = "CASE", sep = "_")

```

Rename columns and rearrange them
```{r}
data <- data %>% 
  rename("age" = "D002_01",
         "gender" = "D003", 
         "student" = "D004", 
         "study" = "D005_01",
         "how_often_do_you_read_news" = "D101",
         "tv2_nyhederne" = "D102_01",
         "dr" = "D102_02",
         "politiken" = "D102_03",
         "information" = "D102_04",
         "berlingske" = "D102_05",
         "jyllands_posten" = "D102_06",
         "b.t" = "D102_07",
         "ekstra_bladet" = "D102_08",
         "dagens.dk" = "D102_09",
         "zetland" = "D102_10",
         "other_media" = "D102_11",
         "gpt3_knowledge" = "D103",
         "hm_answer" = "AA",
         "confidence" = "CO",
         "language_errors" = "LA",
         "factual_errors" = "FA",
         "id" = "CASE",
         "group" = "R001"
         )
```

Make trial column
```{r}
data$trial <- c(rep(01, nrow(data)/16), rep(2, nrow(data)/16),
                rep(3, nrow(data)/16), rep(4, nrow(data)/16),
                rep(5, nrow(data)/16), rep(6, nrow(data)/16),
                rep(7, nrow(data)/16), rep(8, nrow(data)/16),
                rep(9, nrow(data)/16), rep(10, nrow(data)/16),
                rep(11, nrow(data)/16), rep(12, nrow(data)/16),
                rep(13, nrow(data)/16), rep(14, nrow(data)/16),
                rep(15, nrow(data)/16), rep(16, nrow(data)/16))

```

Fix order
```{r}
data[data == "P1"] <- 1
data[data == "P2"] <- 2
data[data == "P3"] <- 3
data[data == "P4"] <- 4
data[data == "P5"] <- 5
data[data == "P6"] <- 6
data[data == "P7"] <- 7
data[data == "P8"] <- 8
data[data == "P9"] <- 9
data[data == "P10"] <- 10
data[data == "P11"] <- 11
data[data == "P12"] <- 12
data[data == "P13"] <- 13
data[data == "P14"] <- 14
data[data == "P15"] <- 15
data[data == "P16"] <- 16

data$order <- ifelse(data$trial == data$IV01_01, 1, 
                     ifelse(data$trial == data$IV01_02, 2,
                            ifelse(data$trial == data$IV01_03, 3,
                                   ifelse(data$trial == data$IV01_04, 4,
                                          ifelse(data$trial == data$IV01_05, 5,
                                                 ifelse(data$trial == data$IV01_06, 6,
                                                        ifelse(data$trial == data$IV01_07, 7,
                                                               ifelse(data$trial == data$IV01_08, 8,
                                                                      ifelse(data$trial == data$IV01_09, 9,
                                                                             ifelse(data$trial == data$IV01_10, 10,
                                                                                    ifelse(data$trial == data$IV01_11, 11,
                                                                                           ifelse(data$trial == data$IV01_12, 12,
                                                                                                  ifelse(data$trial == data$IV01_13, 13,
                                                                                                         ifelse(data$trial == data$IV01_14, 14,
                                                                                                                ifelse(data$trial == data$IV01_15, 15,
                                                                                                                       ifelse(data$trial == data$IV01_16, 16, NA
                            
))))))))))))))))
```

Again deselect columns
```{r}
data <- data %>% 
  select(-IV01_01,-IV01_02,-IV01_03,-IV01_04,
         -IV01_05,-IV01_06,-IV01_07,-IV01_08,
         -IV01_09,-IV01_10,-IV01_11,-IV01_12,
         -IV01_13,-IV01_14,-IV01_15,-IV01_16,
         -time)
```

Create new columns
```{r}
data$hm_correct <- ifelse(data$trial > 8, 2, 1)

data <- data %>% 
  mutate(trial = case_when(trial == "1" ~ "01",
                           trial == "2" ~ "02",
                           trial == "3" ~ "03",
                           trial == "4" ~ "04",
                           trial == "5" ~ "05",
                           trial == "6" ~ "06",
                           trial == "7" ~ "07",
                           trial == "8" ~ "08",
                           trial == "9" ~ "09",
                           TRUE ~ as.character(trial)))

data$article <- paste0("X", data$group, data$trial)

data <- data %>% 
  select(-trial)

data$accuracy <- ifelse(data$hm_correct == data$hm_answer, 1, 0)
```

Fix people that are stupid (jk)
```{r}
data <- data %>% 
  mutate(age = case_when(age == "21 år" ~ "21",
                         TRUE ~ as.character(age)))
data$age <- as.numeric(data$age)
```


Rearrange columns
```{r}
data <- data %>% 
  select(id, gender, age, article, order, hm_answer, hm_correct, accuracy, confidence, language_errors,
               factual_errors, group, MODE, student, study, how_often_do_you_read_news, tv2_nyhederne, dr, politiken, 
               information, berlingske, jyllands_posten, b.t, ekstra_bladet, dagens.dk, zetland, other_media,
               gpt3_knowledge
               )
```



# Early Inspections
Participant counter
```{r}
data %>% 
  group_by(group) %>%
  summarize(n = n()/16)

print(nrow(data)/16)
```

Mean age
```{r}
mean(as.numeric(data$age))
sd(data$age)
```

Mean accuracy on ONLY GPT-3 articles
```{r}
data %>% 
  filter(hm_correct == 2) %>% 
  summarize("How many percent of GPT-3 articles were classified correctly?" = mean(accuracy))


data %>% 
  summarize("How many percent were classified correctly?" = mean(accuracy),
            "Standard Deviation" = sd(accuracy))


```

Seeing which articles that are easiest to identify and hardest
```{r}
easy <- data %>% 
  group_by(article) %>% 
  summarize("Lowest Accuracies" = mean(accuracy)) %>% 
  arrange(`Lowest Accuracies`) %>% 
  head(5)

hard <- data %>% 
  group_by(article) %>% 
  summarize("Highest Accuracies" = mean(accuracy)) %>% 
  arrange(desc(`Highest Accuracies`)) %>% 
  head(5)

print(easy)
print(hard)
rm(easy, hard)
```

Does X perform better than other groups?
```{r}
ggplot(data %>% filter(hm_correct == 2), aes(x = as.factor(gpt3_knowledge), y = accuracy, fill = as.factor(gpt3_knowledge))) +
  geom_bar(stat='summary', fun = 'mean', width=0.7, position=position_dodge()) +
  geom_errorbar(stat='summary', fun.data = mean_se, width=0.4, position=position_dodge(0.7))
```


# Detailed Plotting 
Hit-miss confusion matrix for participant responses
```{r}
confusion <- table(data[,6:7])
confusion <- as_tibble(confusion)

plot_confusion_matrix(confusion,
                      target_col = "hm_correct",
                      prediction_col = "hm_answer",
                      counts_col = "n")


confusion %>% 
  gt(
    rownames_to_stub =  TRUE
  ) %>% 
  gt_theme_nytimes()


# Set up the data frame
df <- data.frame(confusion)
colnames(df) <- c("Predicted", "Actual")

# Create the confusion matrix table
gt(df,
   caption = "Confusion Matrix",
   col_labels = c("Predicted", "Actual"),
   style = cell_text_clip(),
   cell_text = df,
   cell_fill = gt_color_interpolate(color_gradient("white", "steelblue"), df, filter_fun = identity, legend_title = "Value"))

```


Distribution of average accuracies
```{r}
participant_accuracy_distribution <- data %>% 
  group_by(id) %>% 
  summarize(accuracy = mean(accuracy)) %>% 
  ggplot(aes(x = accuracy)) +
  geom_histogram(binwidth = 0.075, color = "#1fc7ad", fill = "#ACF2E7") + 
  scale_x_continuous(limits = c(0.1,0.9), breaks = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1)) +
  scale_y_continuous(breaks = c(0, 5, 10, 15, 20, 25, 30, 35, 40)) + 
  labs(x="PARTICIPANT MEAN ACCURACIES",
       y = "COUNT") +
  theme(text = element_text(family = "Libre Franklin"),
        plot.margin = margin(0.25,0.25,0.5,0.5, "cm"),
        axis.title.x = element_text(vjust = -3),
        axis.title.y = element_text(vjust = 5),
        axis.title = element_text(size = 9, color = "darkgrey", family = "Libre Franklin"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "darkgrey"), 
        axis.ticks = element_line(colour = "darkgrey"))

ggsave(participant_accuracy_distribution, filename = "./figures/participant_accuracy_distribution.png", dpi = 300, type = "cairo", width = 7, height = 7, units = "in")

```

Confidence histogram - how is confidence distributed?
```{r}
plot_data <- data
plot_data$accuracy[plot_data$accuracy == 1] <- "CORRECT"
plot_data$accuracy[plot_data$accuracy == 0] <- "INCORRECT"

confidence_distribution <- ggplot(plot_data, aes(x = as.character(confidence), fill = as.factor(accuracy))) +
  geom_bar(position="stack") +
  scale_fill_manual(values=c("#1fc7ad", "#ACF2E7")) +
  labs(x = "CONFIDENCE",
       y = "COUNT") +
  scale_y_continuous(limits = c(0, 600), breaks = c(0, 100, 200, 300, 400, 500, 600)) + 
  guides(fill=guide_legend(title="Classification\nAccuracy")) +
  theme(text = element_text(family = "Libre Franklin"),
        plot.margin = margin(0.25,0.25,0.5,0.5, "cm"),
        axis.title.x = element_text(vjust = -3),
        axis.title.y = element_text(vjust = 5),
        axis.title = element_text(size = 9, color = "darkgrey"),
        axis.line = element_line(colour = "darkgrey"), 
        axis.ticks = element_line(colour = "darkgrey", size = 0.7),
        legend.title = element_text(size = 11),
        legend.text = element_text(colour = "darkgrey", size = 7),
        legend.position = c(0.92, 0.93),
        panel.background = element_blank())

ggsave(confidence_distribution, filename = "./figures/confidence_distribution.png", dpi = 300, type = "cairo", width = 6, height = 6, units = "in")
```

Does confidence decrease over time?
```{r}
confidence_over_time <- data %>% 
  group_by(order) %>% 
  summarize(confidence = mean(confidence)) %>% 
  ggplot(aes(x = order, y = confidence)) +
  geom_point(color = "#ACF2E7", size = 3) +
  geom_smooth(method = "lm", color = "#1fc7ad", alpha = 0.1, size = 1.5) +
  labs(x = "TRIAL NUMBER",
       y = "CONFIDENCE") +
  scale_y_continuous(limits = c(2.6, 3.4), breaks = c(2.6, 2.8, 3, 3.2, 3.2, 3.4)) + 
  scale_x_continuous(breaks = c(2, 4, 6, 8, 10, 12, 14, 16)) +
  theme(text = element_text(family = "Libre Franklin"),
        plot.margin = margin(0.25,0.25,0.5,0.5, "cm"),
        axis.title.x = element_text(vjust = -3),
        axis.title.y = element_text(vjust = 5),
        axis.title = element_text(size = 9, color = "darkgrey"),
        axis.line = element_line(colour = "darkgrey"), 
        axis.ticks = element_line(colour = "darkgrey", size = 0.7),
        legend.title = element_text(size = 11),
        legend.text = element_text(colour = "darkgrey", size = 7),
        panel.background = element_blank())


ggsave(confidence_over_time, filename = "./figures/confidence_over_time.png", dpi = 300, type = "cairo", width = 6, height = 6, units = "in")

summary(lmerTest::lmer(confidence ~ order + (1|article) + (1|id), data=data))
```

What errors were marked?
```{r}
data$error <- ifelse(data$language_errors == 1 & data$factual_errors == 1, "Both",
                     ifelse(data$language_errors == 1 & data$factual_errors == 2, "Language", 
                            ifelse(data$language_errors == 2 & data$factual_errors == 1, "Factual", "None")))

plot_data <- data
plot_data$hm_answer[plot_data$hm_answer == 2] <- "SYNTHETIC"
plot_data$hm_answer[plot_data$hm_answer == 1] <- "REAL"
  
error_types <- ggplot(plot_data, aes(x = error, group = hm_answer, fill = hm_answer)) + 
  geom_bar(aes(fill = hm_answer)) +
  labs(x = "MARKED ERROR TYPE",
       y = "COUNT") +
  scale_fill_manual(values=c("#1fc7ad", "#ACF2E7")) +
  scale_y_continuous(breaks = c(0, 100, 200, 300, 400, 500, 600, 700)) + 
  guides(fill=guide_legend(title="Participant\nClassification")) +
  facet_wrap(.~hm_correct, labeller = labeller(hm_correct = c("1" = "Real Articles", "2" = "Synthetic Articles"))) +
  theme_bw() +
  theme(text = element_text(family = "Libre Franklin"),
        plot.margin = margin(0.25,0.25,0.5,0.5, "cm"),
        axis.title.x = element_text(vjust = -3),
        axis.title.y = element_text(vjust = 5),
        axis.title = element_text(size = 9, color = "darkgrey"),
        axis.line = element_line(colour = "darkgrey"), 
        axis.ticks = element_line(colour = "darkgrey", size = 0.7),
        legend.title = element_text(size = 11),
        legend.text = element_text(colour = "darkgrey", size = 7),
        legend.position = "right",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(size = 15, face = "bold"))

ggsave(error_types, filename = "./figures/error_types.png", dpi = 300, type = "cairo", width = 8, height = 7, units = "in")
```

```{r}
data$error <- ifelse(data$language_errors == 1 & data$factual_errors == 1, "both errors",
                     ifelse(data$language_errors == 1 & data$factual_errors == 2, "language error", 
                            ifelse(data$language_errors == 2 & data$factual_errors == 1, "factual error", "no error")))

ggplot(data, aes(x = error, group = error, fill = error)) + 
  geom_bar() +
  facet_wrap(.~accuracy, labeller = labeller(accuracy = c("0" = "Actually Human", "1" = "Actually AI"))) +
  ggtitle("What errors were marked when participants answered 'Kunstig Intelligens'")

ggplot(data %>% filter(hm_answer == 1), aes(x = error, group = error, fill = error)) + 
  geom_bar() +
  facet_wrap(.~accuracy, labeller = labeller(accuracy = c("0" = "Actually AI", "1" = "Actually Human"))) +
  ggtitle("What errors were marked when participants answered 'Menneske'")
```

What errors were marked when participants answered "Kunstig intelligens"?
```{r}
data$error <- ifelse(data$language_errors == 1 & data$factual_errors == 1, "both errors",
                     ifelse(data$language_errors == 1 & data$factual_errors == 2, "language error", 
                            ifelse(data$language_errors == 2 & data$factual_errors == 1, "factual error", "no error")))

ggplot(data %>% filter(hm_answer == 2), aes(x = error, group = error, fill = error)) + 
  geom_bar() +
  facet_wrap(.~accuracy, labeller = labeller(accuracy = c("0" = "Actually Human", "1" = "Actually AI"))) +
  ggtitle("What errors were marked when participants answered 'Kunstig Intelligens'")

ggplot(data %>% filter(hm_answer == 1), aes(x = error, group = error, fill = error)) + 
  geom_bar() +
  facet_wrap(.~accuracy, labeller = labeller(accuracy = c("0" = "Actually AI", "1" = "Actually Human"))) +
  ggtitle("What errors were marked when participants answered 'Menneske'")
```

# Statistical Evaluations
Model to see if domain expertise enhances performance
```{r}
# change how_often_do_you_read_news so that we get a baseline which is never instead of often
data_models <- data

data_models$news_consumption <- ifelse(data_models$how_often_do_you_read_news == 1, 5, ifelse(
  data_models$how_often_do_you_read_news == 2, 4, ifelse(
    data_models$how_often_do_you_read_news == 4, 2, ifelse(
      data_models$how_often_do_you_read_news == 5, 1, 3))))

# run model
m1 <- lme4::glmer(accuracy ~ as.factor(news_consumption) + as.factor(gpt3_knowledge) + (1|article), family = binomial, data=data_models)

summary(m1)

boot::inv.logit(0.32738)
boot::inv.logit(0.47842)
```


For classifiers: All articles (average answers)
```{r}
# make 2s into 0s
average_answers <- data
average_answers$hm_answer[average_answers$hm_answer == 2] <- 0
average_answers$hm_correct[average_answers$hm_correct == 2] <- 0

average_answers <- average_answers %>% 
  group_by(article) %>% 
  summarize("human_probability" = mean(hm_answer),
            "true_label" = mean(hm_correct))

average_answers$prediction_human <- ifelse(average_answers$human_probability < 0.5, 0, 1)
average_answers$human_probability <- ifelse(average_answers$prediction_human == 0, 1-average_answers$human_probability, average_answers$human_probability)

#write_csv(average_answers, "human_predictions.csv")
```
